---
author: your_name
title: My first Quarto document
date: today

execute:
  warning: false
  
bibliography: grateful-refs.bib
---

# How to write in markdown


You can write *italic*, ***bold***.
You can also create lists:

-   first item
-   second item

Or numbered lists:

1.    first item
2.    second item

Also, you can create sub-titles:

## Some subtitle

## Some other subtitle

Now that we're familiar with markdown, let's try out some code!

# Loading the packages

Let's start out by loading our necessary *packages*.
As a next step, let's load our data from `palmerpenguins` and have a peek. 

```{r}
#| label: setup
library(tidyverse)
library(palmerpenguins)
library(modelsummary)
library(grateful)
library(here)
library(simplermarkdown)
```

```{r}
#| label: load-data
data(penguins)
head(penguins)
```

# Tables and figures

Let's show a quick plot of some penguin characteristics in @fig-penguins.
@tbl-penguins shows an overview of our penguin characteristics.

```{r}
#| label: fig-penguins
#| fig-cap: Penguin characteristics
ggplot(data = penguins) +
  geom_point(aes(x = bill_length_mm, y = flipper_length_mm, colour = species)) +
  labs(title = "Penguin characteristics",
       caption = "Data from {palmerpenguins}",
       x = "Bill length (mm)",
       y = "Flipper length (mm)",
       col = "Species") +
  theme_minimal()
```
```{r}
#| label: tbl-penguins
#| tbl-cap: The palmerpenguins dataset

penguins |> 
  datasummary_skim()

```

# References

Lastly, we want to show which references we used in this project.

```{r}
#| label: references
#| output: asis
cite_packages(output = "table", out.dir = here()) |> 
  simplermarkdown::md_table()
```

