---
title: Regressions with `fixest` in `R`
subtitle: TU Dresden
author: Sarah

format: 
  revealjs:
    scrollable: true
    self-contained: true
    
execute:
  warning: false
---

```{r}
#| label: setup

library(palmerpenguins)
library(ggplot2)
library(dplyr)
```


## Why regressions?

We can see a relationship, but can't put numbers to it just yet!

```{r}
#| label: fig-scatter
#| fig-cap: Scatter plot
#| echo: false

data(penguins)
penguins |>
  filter(!is.na(sex)) |>
  ggplot() +
  geom_point(aes(bill_length_mm, flipper_length_mm, col = sex)) +
  labs(
    title = "Penguin characteristics",
    caption = "Data source: {palmerpenguins}",
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    col = "Sex"
  )

```

## Ordinary least squares (OLS)

$$
y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \epsilon
$$

We regress the *dependent variable* ($y_i$) on the *independent variables* ($x_1i, x_2i$).
$i$ is the level of observation, e.g. persons or countries.
$\epsilon$ is the error term, $\beta_0$ is a constant.

## Formulas in `R`


How we write it mathematically:

$$
y_i = \beta_0 + \beta_1 x_{1i} + \beta_2 x_{2i} + \epsilon
$$
How we write it in `R`:

```{r}
#| label: some-formula
#| eval: false
#| echo: true

y ~ x1 + x2
flipper_length_mm ~ bill_length_mm + sex
```

## Regression library: `fixest`

```{r}
#| label: first-regression
#| echo: true
library(fixest)

regression_flipper <- feols(flipper_length_mm ~ bill_length_mm + sex, 
                            data = penguins)
regression_bill <- feols(bill_length_mm ~ flipper_length_mm + sex, 
                         data = penguins)
```

## Regression output with `modelsummary` {.smaller}


```{r}
#| label: regression-table
#| echo: true

library(modelsummary)
modelsummary(regression_flipper, stars = TRUE)
```

## Regression outputs of multiple regressions {.smaller}

```{r}
#| label: regression-table-multiple-regresssions
#| echo: true
list(Flipper = regression_flipper,
     Bill = regression_bill) |> 
  modelsummary(stars = TRUE)
```